---
title: "Developing Data Products: Week 2 Assignment"
author: "ij8585"
date: "March 21, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```

## Description

This application visualizes locations visited by a selected technician throughout a selected day.


## Vehicle Tracking Log

The following table depictes raw data from a log file showing the times and lat/lon coordinates of the visited locations.  

```{r inputData, echo=FALSE}

vts <- data.frame(Time = c("08:05","09:35","10:40","12:12","13:55","14:20","15:40","16:21","16:55","17:32"),
                  Location = c("Garage","A","B","C","D","E","F","G","H","I"),
                  Latitude = c(36.993379,37.296120,37.302250,37.304695,37.330444,37.331721,37.333670,37.334025,37.335115,37.367719),
                  Longitude = c(-121.569610,-121.872702,-121.968912,-121.966042,-121.969590,-121.968382,-121.982272,-121.982036,-121.982987,-122.001249   ),
                  Col = c( "blue", "green", "green","green","green", "green", "green","green","green","green")

)
```

 


```{r showData, echo=FALSE, comment = " "}
row.names(vts) <- NULL
head(vts[,-5])

```

## Vehicle Tracking Visualization

The map shows location of the garage from which the technician has been dispatched (blue marker) and locations of the customers visited by the technician throughout the day (green markers). 

```{r tracing, echo=FALSE}

icons <- awesomeIcons(

  iconColor = 'black',

  markerColor = vts$Col,
  text = ifelse(vts$Location == "Garage","",vts$Location )
)


vts %>%
  leaflet(width = "100%") %>%
  addTiles() %>%
  addAwesomeMarkers(~Longitude, ~Latitude,  icon=icons,  label =  ifelse(vts$Location != "Garage", paste("Customer ",vts$Location), "Garage" ), labelOptions = labelOptions(noHide = FALSE), clusterOptions = markerClusterOptions() ) %>%
  addLegend(labels = c("Garage","Customers"), colors = c("blue", "green"))

```

Enjoy it!
