---
title: "Developing Data Products: Week 4 Assignment"
author: "ij8585"
date: "April 07, 2017"
output: ioslides_presentation
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Application Description

This is simple data exploration application which presents the following information about a selected dataset:

* data summary
* data view
* observations 



The application has been implemented in Shiny using RStudio and is hosted on the
[ShinyApps.io](https://ij8585.shinyapps.io/coursera/). The R source code is available at [GitHub](https://github.com/ij8585/ddp).


There are currently three datasets available for data exploration: *cars*, *pressure*, *women*

## Data Summary

The basic statistics are computed using **summary** function i.e.:

```{r r1, echo=TRUE, comment = " ", eval=TRUE}
    summary(pressure)
```

In the Shiny server.R file the function is invoked as follows


```{r r2, echo=TRUE, comment = " ", eval=FALSE, size="small"}
  output$summary <- renderPrint({ summary( datasetInput()) })
```

*Note: The summary is based on the full dataset.*


## Data View
###### The data points are visualized using **plot** function and **lowess** function is used to calculate the smoother line.
```{r dv, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 5,  fig.height = 4,  fig.align="center"}
plot(cars, xlab = "Speed", ylab = "Stopping distance", las = 1)
lines(lowess(cars$speed, cars$dist, f = 2/3, iter = 3), col = "red")
```
  
###### *Note: the size of the points and color of the line can be changed in the application using the widgets in the control panel.*
  

## Observations

The observations are displayed using **head** function i.e.:

```{r ob1, echo=TRUE, comment = " ", eval=TRUE}
    head(pressure,5)
```

In the Shiny server.R file the function is invoked as follows

```{r ob2, echo=TRUE, comment = " ", eval=FALSE, size="small"}
  output$view <- renderTable({ head(datasetInput(), n = input$obs) })
```

*Note: the number of the displayed observations can be changed in the control panel.*  

 
  
